---
title: "hypothesis_test"
output: html_document
date: "2023-08-30"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#1. A random sample of 12 subjects was taken from a target population to study the prevalence of a disease p. It turned out that 3 of them were diseased. 
##(a) Estimate the disease prevalence p.

```{r 1. (a)}
sample_size <- 12
diseased_count <- 3
estimated_p <- diseased_count / sample_size
estimated_p
```

##(b) Use asymptotic procedures to test H0 : p = 0.6 vs. Ha : p \> 0.6. (1)

```{r 1. (b)}
null_p <- 0.6
z_stat <- (estimated_p - null_p) / sqrt(null_p * (1 - null_p) / sample_size)
p_value <- 1 - pnorm(z_stat)
p_value
if (p_value <= 0.05) {
  cat("Reject the null hypothesis.\n")
} else {
  cat("Accept the null hypothesis.\n")
}
```

##(c) Change Ha : p \> 0.6 in (1) to Ha : p \< 0.6 and repeat b).

```{r 1. (c)}
null_p <- 0.6
z_stat_alt <- (estimated_p - null_p) / sqrt(null_p * (1 - null_p) / sample_size)
p_value_alt <- pnorm(z_stat_alt)
p_value_alt
if (p_value_alt <= 0.05) {
  cat("Reject the null hypothesis.\n")
} else {
  cat("Accept the null hypothesis.\n")
}
```

##(d) Change Ha : p \> 0.6 in (1) to Ha : p 6= 0.6 and repeat b).

```{r}
two_sided_p_value <- 2 * pmin(p_value, 1 - p_value)
two_sided_p_value
if (two_sided_p_value <= 0.025) {
  cat("Reject the null hypothesis.\n")
} else {
  cat("Accept the null hypothesis.\n")
}
```
#2. Since the sample size in Problem 1 is not very large, it is better to use exact tests.
##(a) Apply exact tests to test the hypothesis in (1) for the data in Problem 1, andcompare your results with those derived from asymptotic tests.
```{r}
x <- 3  
n <- 12  
p0 <- 0.6 
binom_test_result <- binom.test(x, n, p = p0, alternative = "greater")
p_value_binom_greater <- binom_test_result$p.value
p_value_binom_greater
if (p_value_binom_greater <= 0.05) {
  cat("Reject the null hypothesis.\n")
} else {
  cat("Accept the null hypothesis.\n")
}
```
##(b) Change Ha : p > 0.6 in (1) to Ha : p < 0.6 and repeat a).
```{r}
x <- 3  
n <- 12  
p0 <- 0.6 
binom_test_result <- binom.test(x, n, p = p0, alternative = "less")
p_value_binom_less <- binom_test_result$p.value
p_value_binom_less
if (p_value_binom_less <= 0.025) {
  cat("Reject the null hypothesis.\n")
} else {
  cat("Accept the null hypothesis.\n")
}
```
##(c) Change Ha : p > 0.6 in (1) to Ha : p 6= 0.6 and repeat a).
```{r}
x <- 3  
n <- 12  
p0 <- 0.6 
binom_test_result <- binom.test(x, n, p = p0, alternative = "two.sided")
p_value_binom_twoside <- binom_test_result$p.value
p_value_binom_twoside
if (p_value_binom_twoside <= 0.025) {
  cat("Reject the null hypothesis.\n")
} else {
  cat("Accept the null hypothesis.\n")
}
```
#In the DOS study, we are interested in testing the following hypothesis concerning the distribution of depression diagnosis for the entire sample:
Pr(No depression) = 0.65
Pr(Minor depression) = 0.3
Pr(Major depression) = 0.05
##(a) Use the chi-square test to test the hypothesis.
```{r}
expected <- c(0.65, 0.3, 0.05)
observed <- c(481, 136, 128)
result_chisq <- chisq.test(observed, p = expected)
print(result_chisq)
```

##(b) Use the exact test to test the hypothesis.
```{r}
result_exact_chisq <- multinomial.test(observed, p = expected, simulate.p.value = TRUE)
print(result_exact_chisq)
```

